Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-30 Paper/ms.tex
invariance

In data analysis problems, phase transitions can exist when the data contains
a ``big'' effect which provides a lot of information about some parameters, and
a ``small'' subtle effect.
Nested Sampling, and variants such as DNS, are not affected
by phase transitions because the exploration only makes use of likelihood
{\it rankings}, rather than likelihood values themselves.
Part of their output, the relationship between the
likelihood $L$ and the enclosed prior mass
$X(L) = \int \pi(\theta) \mathds{1}\left[L(\theta) > L\right]\, d^n\theta$
can be used to diagnose whether the
problem contains a phase transition. In particular, if the graph of $\log(L)$
vs. $\log(X)$ is convex at some point, then a phase transition exists
\citep{skilling}.

>>>>

In data analysis problems, phase transitions can exist when the data contains
a ``big'' effect which provides a lot of information about some parameters, and
a ``small'' subtle effect.
Nested Sampling, and variants such as DNS, are not affected
by phase transitions because the exploration only makes use of likelihood
{\it rankings}, rather than likelihood values themselves, and are therefore
invariant under monotonic transformations of the likelihood function.
Part of their output, the relationship between the
likelihood $L$ and the enclosed prior mass
$X(L) = \int \pi(\theta) \mathds{1}\left[L(\theta) > L\right]\, d^n\theta$
can be used to diagnose whether the
problem contains a phase transition. In particular, if the graph of $\log(L)$
vs. $\log(X)$ is convex at some point, then a phase transition exists
\citep{skilling}.
